Clustering in a hyperbolic model of complex networks.

### 2019-05-01 proofs_infinite_k.tex
processed most of Nikolaos comments on sections 5-7

In this section we explain the challenges with each step and give a detailed overview of the structure for the proof of Theorem~\ref{thm:mainktoinfty} using intermediate results for each of the steps. To this end we define the scaling function
\begin{equation}\label{eq:def_scaling_function}
	s(k) = \begin{cases}
		k^{-(4\alpha - 2)} &\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
		\log(k) k^{-1} &\mbox{if } \alpha = \frac{3}{4},\\
		k^{-1} &\mbox{if } \alpha > \frac{3}{4},
	\end{cases}
\end{equation}
so that $\gamma(k) = \bigT{s(k)}$ as $k \to \infty$. We will end this section with the proof of Theorem~\ref{thm:mainktoinfty}, based on the intermediate results.

@@

In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a(k)^-, a(k)^+]$, with
\[
	a(k)^\pm = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
\]
The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and Poisson random variables are well concentrated around their mean, i.e. around heights $y$ for which $\mu(y) \approx k$. Since $\mu(y) = \mu(\BallPo{y}) = \xi e^{y/2}$, this implies that integration with respect to $\rho(y,k)$ is concentrated around $y \approx 2\log(k/\xi)$. In the remainder of this paper we will often encounter integrands involving the function $\Prob{\Po(\mu_n(y)) = k}$, for some $\mu_n(y)$ which is asymptoticly equivalent to $\mu(y)$. In these case we also want to be able to restrict our integration around those heights $y$ for which $y \approx 2\log(k_n/\xi)$. Such results are established in Section~\ref{sec:concentration_argument}. Moreover, we prove that if $\mu_n$ corresponds to either $\Mu{\BallHyp{y}}$ or $\Mu{\BallPon{y}}$, then for a certain classs of functions $h$
\[
	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y 
	= (1+\smallO{1}) \int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
\]
i.e. we may replace $\hat{\rho}_n(y,k_n)$ in the integrand with $\rho(y,k_n)$.

@@

Recall that the first step for the fixed $k$ case was to show that the transition from the KPKVB graph $G_n = G(n;\alpha,\nu)$ to the Poissonized version $\GPo$ did not influence clustering. Here we first make a transition from the local clustering function $c(k_n; G_n)$ to the adjusted version $c^\ast(k_n; G_n)$. The following lemma justifies working with this modified version. The proof uses a concentration result for $\N_{n}(k_n)$ and full details can be found in Section~\ref{ssec:coupling_H_HP}.

@@

Assuming this concentration result, we are left to compute the limit of $\Exp{c^\ast(k_n; \Gbox)}$ as $n \to \infty$ and show that it is equivalent to $\gamma(k_n)$. To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of $c^\ast(k;\Gbox)$ and $\gamma(k_n)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.

>>>>

In this section we explain the challenges associated with each step and give a detailed overview of the structure for the proof of Theorem~\ref{thm:mainktoinfty} using intermediate results for each of the steps. To this end we define the scaling function
\begin{equation}\label{eq:def_scaling_function}
	s(k) = \begin{cases}
		k^{-(4\alpha - 2)} &\mbox{if } \frac{1}{2} < \alpha < \frac{3}{4},\\
		\log(k) k^{-1} &\mbox{if } \alpha = \frac{3}{4},\\
		k^{-1} &\mbox{if } \alpha > \frac{3}{4},
	\end{cases}
\end{equation}
so that $\gamma(k) = \bigT{s(k)}$ as $k \to \infty$. We will end this section with the proof of Theorem~\ref{thm:mainktoinfty}, based on the intermediate results.

@@

In the proof of Proposition~\ref{prop:asymp} we used a result that allowed us to restrict integration over $y$ to the interval $[a^-(k), a^+(k)]$, with
\[
	a^\pm(k) = 2\log\left(\frac{k \pm C \sqrt{k \log(k)}}{\xi} \vee 1\right).
\]
The reason for this was that the integrand included the function $\rho(y,k) = \Prob{\Po(\mu(y)) = k}$, where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$ and Poisson random variables are well concentrated around their mean, i.e. around heights $y$ for which $\mu(y) \approx k$. Since $\mu(y) = \mu(\BallPo{y}) = \xi e^{y/2}$, this implies that integration with respect to $\rho(y,k)$ is concentrated around $y \approx 2\log(k/\xi)$. In the remainder of this paper we will often encounter integrands involving the function $\Prob{\Po(\mu_n(y)) = k_n} := \hat{\rho}_n(y,k_n)$, for some $\mu_n(y)$ which is asymptoticly equivalent to $\mu(y)$. In these cases we also want to be able to restrict our integration around those heights $y$ for which $y \approx 2\log(k_n/\xi)$. Such results are established in Section~\ref{sec:concentration_argument}. Moreover, we prove that if $\mu_n$ corresponds to either $\Mu{\BallHyp{y}}$ or $\Mu{\BallPon{y}}$, then for a certain classs of functions $h$
\[
	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y 
	= (1+\smallO{1}) \int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
\]
i.e. we may replace $\hat{\rho}_n(y,k_n)$ in the integrand with $\rho(y,k_n)$.

@@

Recall that the first step for the fixed $k$ case was to show that the transition from the KPKVB graph $G_n = G(n;\alpha,\nu)$ to the Poissonized version $\GPo$ did not influence clustering. Here we first make a transition from the local clustering function $c(k_n; G_n)$ to the adjusted version $c^\ast(k_n; G_n)$. The following lemma justifies working with this modified version. The proof uses a concentration result for $N_{n}(k_n)$ and full details can be found in Section~\ref{ssec:coupling_H_HP}.

@@

Assuming this concentration result, we are left to compute expectation $\Exp{c^\ast(k_n; \Gbox)}$ and show that it is asymptotically equivalent to $\gamma(k_n)$ as $n \to \infty$. To accomplish this we move to the infinite limit model $\Ginf$ and show that the difference between the expected value of $c^\ast(k;\Gbox)$ and $\gamma(k_n)$ goes to zero faster than the proposed scaling in Theorem \ref{thm:local_clustering_hyperbolic}.
